Untitled

### 2025-02-25 script/r/draft.Rmd
Add mountains. Geo ctrls script done

binary_raster <- ifel(!is.na(desert_wgs84), 1, 0)

@@

africa_extent <- ext(-20, 60, -40, 40)

@@

>>>>

africa_extent <- ext(-30, 60, -40, 40)

destert_africa <- crop(desert_wgs84, africa_extent)

binary_raster <- ifel(!is.na(desert_africa), 1, 0)

@@

africa_extent <- ext(-30, 60, -40, 40)

@@

```{r}
tiff_file <- "data/data_raw/geography/mountain/k3binary.tif"

mountain_wgs84 <- rast(tiff_file)

print(mountain_wgs84)

africa_extent <- ext(-30, 60, -40, 40)

mountain_africa <- crop(mountain_wgs84, africa_extent)

binary_raster <- ifel(!is.na(mountain_africa), 1, 0)

plot(binary_raster, main = "mountain Map of Africa", col = viridis(100))

mountain_adm1_df <- data.frame()

  mountain_adm1 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')

  regions$mountain_adm1 <- mountain_adm1

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, mountain_adm1)

  mountain_adm1_df <- rbind(mountain_adm1_df, country_results)
}

mountain_adm1_df %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(mountain_adm1_df))

saveRDS(mountain_adm1_df, file="data/data_rds/geo_ctrl/mountain_adm1.rds")

mountain_adm2_df <- data.frame()

  mountain_adm2 <- exactextractr::exact_extract(binary_raster_masked, regions, 'mean')

  regions$mountain_adm2 <- mountain_adm2

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, mountain_adm2)

  mountain_adm2_df <- rbind(mountain_adm2_df, country_results)
}

mountain_adm2_df %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(mountain_adm2_df))

saveRDS(mountain_adm2_df, file="data/data_rds/geo_ctrl/mountain_adm2.rds")
```
